Finding Optimal Sequences for Area Aggregation---\protect\\ \Astar vs. Integer Linear Programming

### 2020-07-01 area_agg_seq_tsas.tex
Some small changes; also removed pdf file from repo.

\begin{document}
\title
[Finding Optimal Sequences for Area Aggregation] %short title
{Finding Optimal Sequences for Area Aggregation---\texorpdfstring
    {\Astar vs.\ Integer Linear Programming} %title of the paper
    {A* vs.\ Integer Linear Programming} %title of the pdf
}

@@

\begin{figure}[tb]
\centering
\includegraphics[page=1]{AreaAgg_NPHard}
\caption{The reduction for our NP-hardness proof.
    The dashed polygon in (c) shows 
    the merged vertices.}
\label{fig:AreaAgg_Reduction}
\end{figure}

We define the weights of the vertices 
in \fig\ref{fig:AreaAgg_Reduction}b as follows:
\begin{itemize}
\item Every white vertex has weight~$1$.
\item Every black vertex has weight~$2$.
\item Every gray vertex has weight~$2|V_\mathrm{A}| + 2|E_\mathrm{A}|$,
which is equal to the total weight of all white and black vertices.
\end{itemize}
When we merge two vertices, 
the weight of the new vertex is the sum of the two.
In each aggregation step, 
we require the smallest area to be aggregated with one of its neighbors.
The area sizes correspond to the weights of the vertices in \fig\ref{fig:AreaAgg_Reduction}b.   
Therefore, our definition of the weights to a certain degree determines 
the order in which the vertices are selected:
\begin{itemize}
\item \emph{Phase I}: In each of the first~$2|E_\mathrm{A}|$ steps, 
a white vertex is selected and merged with one of its neighbors, 
such that the white vertex receives the neighbor's color or vice versa
(\fig\ref{fig:reduction2} shows a possible result).
\item \emph{Phase II}: In each of the next~$|V_\mathrm{A}|$ steps, 
a non-gray vertex is selected and merged with one of its neighbors.
\item \emph{Phase III}: $|V_\mathrm{A}|-1$ steps remain to reach the goal map.
\end{itemize}

@@

\begin{figure}[tb]
\centering
\includegraphics[page=2]{AreaAgg_NPHard}
\caption{The situation after Phase I has been conducted 
    such that all black vertices corresponding to a vertex cover 
    of~$G_\mathrm{A}$ have been recolored white.
    The dashed polygons show that the vertices are merged.}
\label{fig:reduction2}
\end{figure}
\end{proof}

@@

\begin{figure}[tb]
%\captionsetup[subfigure]{labelformat=empty}
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics[page=1]{AreaAgg_Data}
\caption{Start map, $5{,}537$ polygons, \\
	at scale $1:50{,}000$}
\end{subfigure}
\hfill
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics[page=2]{AreaAgg_Data}
\caption{Goal map, $734$ polygons, \\
	at scale $1:250{,}000$}
\end{subfigure}
%
%It doesn't work to directly use 
%\vspace{\baselineskip} for subfigures.
\par\vspace{\baselineskip} %Leave a gap	figures
%
\begin{subfigure}{\textwidth}
\centering
\includegraphics[page=3]{AreaAgg_Data}
\caption{The 20 land-cover types appearing in our data}
\end{subfigure}
\caption{The data of our case study.}
\label{fig:AreaAgg_Data}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[page=4]{AreaAgg_Data}
\caption{Distribution of the region sizes:
	the $y$-axis shows how many regions 
	of a given size range are contained in our dataset.}
\label{fig:AreaAgg_NumRegion}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[page=5]{AreaAgg_Data}
\caption{The tree of type hierarchy used in our case study.
	For example, the distance between 
	types \emph{village} and \emph{farm land} is~$6$.}
\label{fig:AreaAgg_TypeDistances}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[page=3]{AreaAgg_CaseStudy2_Plot}
\caption{The number of regions for which
	our ILP found optimal, feasible, or no solutions 
	when using time limits~$100\,$s and~$200\,$s.
	Using more time, our ILP was able to 
	solve more instances to optimality.}
\label{fig:AreaAgg_CaseStudy2_ILP}
\end{figure}

>>>>

\begin{document}
\title
[Finding Optimal Sequences for Area Aggregation] %short title
{Finding Optimal Sequences for Area Aggregation---\\
  \texorpdfstring
    {\Astar vs.\ Integer Linear Programming} %title of the paper
    {A* vs.\ Integer Linear Programming} %title of the pdf
}

@@

\begin{figure}[tb]
\centering
\includegraphics[page=1]{AreaAgg_NPHard}
\caption{Our NP-hardness reduction.  The dashed area in~(c) represents
  the vertices that are merged.}
\label{fig:AreaAgg_Reduction}
\end{figure}

We define the weights of the vertices 
in \fig\ref{fig:AreaAgg_Reduction}b as follows:
\begin{itemize}
\item Every white vertex has weight~$1$.
\item Every black vertex has weight~$2$.
\item Every gray vertex has weight~$2|V_\mathrm{A}| + 2|E_\mathrm{A}|$,
which is equal to the total weight of all white and black vertices.
\end{itemize}
When we merge two vertices, 
the weight of the new vertex is the sum of the two.
In each aggregation step, 
we require the smallest area to be aggregated with one of its neighbors.
The area sizes correspond to the weights of the vertices in \fig\ref{fig:AreaAgg_Reduction}b.   
Therefore, our definition of the weights to a certain degree determines 
the order in which the vertices are selected:
\begin{description}[leftmargin=1.7cm,style=sameline]
\item[\emph{Phase I}:] In each of the first~$2|E_\mathrm{A}|$ steps, 
a white vertex is selected and merged with one of its neighbors, 
such that the white vertex receives the neighbor's color or vice versa
(\fig\ref{fig:reduction2} shows a possible result).
\item[\emph{Phase II}:] In each of the next~$|V_\mathrm{A}|$ steps, 
a non-gray vertex is selected and merged with one of its neighbors.
\item[\emph{Phase III}:] $|V_\mathrm{A}|-1$ steps remain to reach the goal map.
\end{description}

@@

\begin{figure}[tb]
\centering
\includegraphics[page=2]{AreaAgg_NPHard}
\caption{The situation after Phase I has been conducted 
    such that all black vertices corresponding to a vertex cover 
    of~$G_\mathrm{A}$ have been recolored white.
    The dashed areas represent the vertices that are merged.}
\label{fig:reduction2}
\end{figure}
\end{proof}

@@

\begin{figure}[tb]
%\captionsetup[subfigure]{labelformat=empty}
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics[page=1]{AreaAgg_Data}
\caption{Start map, $5{,}537$ polygons, \\
	at scale $1:50{,}000$}
\end{subfigure}
\hfill
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics[page=2]{AreaAgg_Data}
\caption{Goal map, $734$ polygons, \\
	at scale $1:250{,}000$}
\end{subfigure}

\bigskip
\bigskip

\begin{subfigure}{\textwidth}
\centering
\includegraphics[page=3]{AreaAgg_Data}
\caption{The 20 land-cover types appearing in our data}
\end{subfigure}
\caption{The data of our case study.}
\label{fig:AreaAgg_Data}
\end{figure}

%\begin{figure}[p]
%\begin{minipage}{\textwidth}
\begin{figure}[tb]
\centering
\includegraphics[page=4]{AreaAgg_Data}
\caption{Distribution of the region sizes:
	the $y$-axis shows how many regions 
	of a given size range are contained in our dataset.}
\label{fig:AreaAgg_NumRegion}
\end{figure}
% \end{minipage}

%\begin{minipage}{\textwidth}
\begin{figure}[tb]
\centering
\includegraphics[page=5]{AreaAgg_Data}
\caption{The tree of type hierarchy used in our case study.
	For example, the distance between 
	types \emph{village} and \emph{farm land} is~$6$.}
\label{fig:AreaAgg_TypeDistances}
\end{figure}
%\end{minipage}
%\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[page=3]{AreaAgg_CaseStudy2_Plot}
\caption{The number of regions for which
	our ILP found optimal, feasible, or no solutions 
	when using time limits~$100\,$s and~$200\,$s.
	Using twice the time, our ILP was able to 
	solve only 5.8$\,$\% more instances to optimality.}
\label{fig:AreaAgg_CaseStudy2_ILP}
\end{figure}
